\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm} LFEUI - Investigation Proposal \\ \vspace{4mm} {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-1mm}

### 2023-12-02 text/proposta/prop.tex
logbook 1

\vspace{-5mm}

@@

@@

Our project will be focused on the detection of Li in technological materials through nuclear reactions. The main motivation for this project is to study and develop a detection technique for elements such as Li and Br with high sensitivity.

@@

The experimental set-up consists of a Tandem accelerator, a beam line with an electromagnet and a chamber with the samples and the detectors.
The accelerator produces a beam of protons with a kinetic energy of 5 MeV which is deviated by the electromagnet and hits the samples. 
The electromagnets deflect particles with different angles according to their charge-to-mass ratio.
This allows us to remove any unwanted particles from the beam and only let the protons pass through.
The detectors used are silicon detectors - these detect charged particles through the ionization they produce in the silicon.

@@

@@

Experimental conditions requiring special safety precautions such as the use of lasers, high pressure cells, bacteria, dangerous substances, toxic substances and radioactive materials, must be identified in the proposal.

@@

\begin{table}[H]
\centering
\begin{tabular}{|w{0.45\linewidth}|w{0.3\linewidth}|w{0.15\linewidth}|}
\hline
Phase & Date & Duration \\ \hline
Theoretical Background, Planning and Lab Overview & 30/11/2023 9h30 & 4h \\ \hline
Experiment & 7/12/2023 8h00 & 8h \\ \hline
Results Discussion & ?? 9h30 & 4h \\ \hline
\end{tabular}
\end{table}

>>>>

\vspace{-8mm}

\begin{center}
  \textbf{\Large Abstract}
\end{center}

% \begin{abstract}
%   \par textvtgerthrt
% \end{abstract}

\par In the following document we present a proposal for a scientific research being developed

\vspace{4.0mm}

@@

\paragraph{Goal}

@@

Our project will be focused on the detection of Li in technological materials through nuclear reactions.
The main motivation for this project is to study and develop a detection technique for elements such as Li with
high sensitivity.

\paragraph{Scientific Background}

@@

The experimental set-up consists of a Tandem accelerator, a beam line with an electromagnet and a chamber with the samples
and the detectors.
The accelerator produces a beam of protons with a kinetic energy of up to 5 MeV which is deviated by the electromagnet
and hits the samples. 
The electromagnets deflect particles with different angles according to their charge-to-mass ratio.
This allows us to remove any unwanted particles from the beam and only let the protons pass through.
The detectors used are silicon detectors - these detect charged particles through the ionization they produce in the
silicon.

@@

\paragraph{WorkPlan}

Obtaining the energy spectrum of the alpha particles resulting from the reaction between the protons and the samples will
evolve the following steps:

\begin{enumerate}
  \item Accelerator Startup;
  \item Calibration of the detectors with a sample of known composition;
  \item Obtaining the energy spectrums of both samples;
  \item Analysis of the results.
\end{enumerate}

\paragraph*{Beam Energy}

In order to choose the energy of the beam we need to take into account the cross section of the reaction between the the protons and the Li-7. We

\begin{center}
  \includegraphics[width=0.95\linewidth]{../images/Li_crosssection_energy.jpeg}
  \captionof{figure}{Cross section of the reaction between protons and Li-7 as a function of the beam energy.}
\end{center}

@@

During the experiments, the accelerator will be producing a beam of protons with a kinetic energy of up to 5 MeV. Because of this there will be a high radiation level near the accelerator.
There are radiation maps that show the radiation levels in different areas of the laboratory.

@@

\begin{table}[H]
\centering
\begin{tabular}{|w{0.4\linewidth}|w{0.3\linewidth}|w{0.15\linewidth}|}
\hline
Phase & Date & Duration \\ \hline
Theoretical Background, Planning and Lab Overview & 30/11/2023 9h30 & 4h \\ \hline
Experiment & 7/12/2023 8h00 & 8h \\ \hline
Results Discussion & ?? 9h30 & 4h \\ \hline
\end{tabular}
\end{table}
